---
output: rmarkdown::github_document
---

# elpresidente

## Description

Methods are provided that let you search and extract corpus elements 
from 'The American Presidency Project' <http://www.presidency.ucsb.edu>.
    
## What's Inside The Tin

The following functions are implemented:

- `app_eo_list`:	Retieve a data frame of metadata about Executive Orders issues in a given year
- `app_get_eo`:	Retrieve metadata and full text of an executive order by APP id

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/elpresidente")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(elpresidente)

# current verison
packageVersion("elpresidente")

```

## Example

```{r message=FALSE, warning=FALSE, error=FALSE}
library(purrr)
library(tidyr)
library(dplyr)

app_eo_list(1826) %>%
  mutate(eo_info = map(eo_id, app_get_eo)) %>%
  unnest() %>%
  glimpse()

app_eo_list(2014) %>%
  mutate(eo_info = map(eo_id, app_get_eo)) %>%
  unnest() %>%
  glimpse()
```